Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-07-06 latex/CEUR/paper.tex
Removed a few more reference to pixel prior models in text since there isn't room to compare superpixel/pixel prior in this paper

\section{Results and analysis}
\label{sec::results}
\subsection{Data}
A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
The ground truth labels in this dataset describe 20 different urban land cover/land use classes (i.e. $K=20$) as well as an unlabelled state, described as Unclassified.
The modes of input data represent measurements from three sensor types: LiDAR, optical and hyperspectral (HS).
The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT).
In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.

@@

In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block.
Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any particularly large contiguous blocks from skewing its set into having an over-representation of that class (see Figure \ref{fig::dataset_split} for a visual depiction of a random split).
The set of contiguous blocks obtained after splitting along these arbitrary grid lines were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively.
This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.

\begin{figure}[!t]
\centering
\includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
\caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
\label{fig::dataset_split}
\end{figure}

@@

In the results presented, two classes were randomly selected to act as OOD.
This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation of performance presented.
Each model type was assessed over the same 10 sampled OOD class pairs for fairness.
The AUROC and AUPR values measured can be found in Table \ref{tab::ood_auroc} and Table \ref{tab::ood_aupr} respectively.

@@

As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is the highest ranked model.
Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
The performance of the S-BGCN-T-K model trained using the pixel prior stands out above the performance of other models trained.
This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.

>>>>

\section{Results and analysis}
\label{sec::results}
\subsection{Data}
A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods.
The ground truth labels in this dataset describe 20 different urban land cover/land use classes (i.e. $K=20$) as well as an unlabelled state, described as Unclassified.
The modes of input data represent measurements from three sensor types: LiDAR, optical and hyperspectral (HS).
The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT).
In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.

@@

% In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block.
% Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any prevent large contiguous blocks from skewing class balances between sets (see Figure \ref{fig::dataset_split} for a depiction of a random split).
% The resulting set of blocks were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively.
% This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.
% 
% \begin{figure}[!t]
% \centering
% \includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
% \caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
% \label{fig::dataset_split}
% \end{figure}

@@

In the results presented, two classes were randomly selected to act as OOD.
This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation computed.
Each model type was assessed over the same 10 sampled OOD class pairs for fairness.
The AUROC and AUPR values measured can be found in Table \ref{tab::ood_auroc} and Table \ref{tab::ood_aupr} respectively.

@@

As for the task of misclassification detection, the S-BGCN-T-K model is the highest ranked model.
Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
The performance of the S-BGCN-T-K model stands out above the performance of other models trained.
This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.
